---
title: "GRIP-Data Science & Business Analytics Tasks"
author: "Done By: Safa AL-Shafie"
date: "2023-04-04"
output: html_document
---

## Task #1/Prediction using Supervised ML

In this task we will predict:

* 1-The Score percentage of students based on the study hours.
* 2-The Student's score for 9.25 hrs of studying.

*Dataset:*<https://drive.google.com/file/d/1koGHPElsHuXo9HPL4BQkZWRMJkOEHiv4/view>

## Setting up the Environment
```{r install & load packages, warning=FALSE}
#install.packages("tidyverse")
library(tidyverse)
library(ggplot2)
library(readr)
library(dplyr)
#install.packages("ggpubr")
library(ggpubr)
```

## preparing & exploring data
```{r exploring data}
df <- read_csv("D:/data analysis workshop/spark foundation/#1/dataset/Book1.csv")
```
```{r}
colnames(df)
```

```{r data}
head(df)
```

```{r plotting data}
plot(df)
```

## Exploring Scores-Hours variables correlation
```{r Scores-Hours Correlation}
df%>%
  summarise(cor(scores,hours))
```

## creating the model
```{r crating & investigating the regression model}
model<- lm(scores~hours, data = df)
summary(model)
```

## models attributes
```{r attributes}
attributes(model)
model$coefficients
model$residuals
model$model
```

## Visualize the regression model
```{r model graph, warning=FALSE}
ggplot(df, aes(x=hours,y=scores))+
  geom_point()+
  geom_smooth(mapping = aes(x=hours,y=scores),method='lm', se=0, color= "red",lwd=2)+
  labs(title = 'Scores Percentage vs. Study Hours')+
  theme_classic()+
  stat_regline_equation(label.x=1,label.y=80,aes(label= ..eq.label..), color="darkgreen",lwd=2)+
  annotate('text',x=1.85,y=75,label="p-value: < 2.2e-16", color="darkgreen")+
  stat_regline_equation(label.x=1,label.y=70,aes(label= ..rr.label..), color="darkgreen")
```


## Finding the student score when the study hour is 9.25
```{r 9.25 hours of studying}
score_for_9.25_studing_hours<-predict(model, data.frame(hours=9.25))
score_for_9.25_studing_hours
```

## Creating new data frame with predicted values
```{r new dataset}
df1<- df %>%
  mutate(predicted_score=predict(model))%>%
  add_row(hours=9.25, predicted_score = score_for_9.25_studing_hours)
```

```{r new Dataset}
head(df1,26)
```

